---
title: "AnaliseDuolingo"
author: "eduardovitor"
date: "`r Sys.Date()`"
output: md_document
---

```{r}
 library(tidyverse)
 library(dplyr)
 library(lubridate)
```

## Reading dataframe file containing a cronological record of minutes of practice on Duolingo
   Check : Minutes count x 1000
```{r}

  workdir ="/home/eduardovitor/Downloads/Loop Habits CSV 2022-11-11/001 Duolingo ingls/"
  checkmarks = paste(workdir,"Checkmarks.csv",sep="")
  df_checkmarks = read_csv(checkmarks)
  df_checkmarks$check <- df_checkmarks$check/1000
```
## Understanding dataframe structure
```{r}
  str(df_checkmarks)
```
## Converting date column to class
```{r}
df_checkmarks$date <- as.Date(df_checkmarks$date,
                        format = "%y-%m-%d")
class(df_checkmarks$date)
```
## Getting data of year, month and day
```{r}
  df_checkmarks <- df_checkmarks %>% mutate(month=month(date,label=TRUE),year=year(date),day=day(date))
```
## Removing November month because this month's data is incomplete
```{r}
  df_checkmarks <- df_checkmarks %>% filter(month!="Nov")
```

## Boxplots grouping data on practice time by month
```{r}
  df_checkmarks %>% 
  group_by(month) %>% 
  ggplot(aes(x = month, y=check, fill=month)) +
  geom_boxplot()+
  theme_minimal()+
  theme(legend.position = "none")+
  labs(x="", y="Minutes", title = "Duolingo English practice time grouped by month (2022)")
```
  
## Line graph showing practice time throughout the months
```{r}
  df_checkmarks %>% 
  ggplot(aes(x = date, y=check)) +
  theme_minimal()+
  geom_line()+
  geom_point()+
  labs(x="", y="Minutes per day", title="Duolingo English practice time in 2022 (Jan - Oct)")
```

## Plot showing English practice time during my vacation month
```{r}
df_checkmarks %>% 
  ggplot(aes(x = date, y=check)) +
  theme_minimal()+
  geom_line()+
  geom_point()+
  scale_x_date(limit=c(as.Date("2022-01-01"),as.Date("2022-01-31")))+
  labs(x="", y="Minutes per day", title="Duolingo English practice time during January")
```
## Plot showing English practice time during a regular month in my routine (June)

```{r}
df_checkmarks %>% 
  ggplot(aes(x = date, y=check)) +
  theme_minimal()+
  geom_line()+
  geom_point()+
  scale_x_date(limit=c(as.Date("2022-06-01"),as.Date("2022-06-30")))+
  labs(x="", y="Minutes per day", title="Duolingo English practice time during June")
```
## Plot showing English practice time during a busy month in my routine (October)

```{r}
df_checkmarks %>% 
  ggplot(aes(x = date, y=check)) +
  theme_minimal()+
  geom_line()+
  geom_point()+
  scale_x_date(limit=c(as.Date("2022-10-01"),as.Date("2022-10-31")))+
  labs(x="", y="Minutes per day", title="Duolingo English practice time during October")
```

## Understanding practice time data distribution with scatterplot

```{r}
 df_checkmarks %>% 
  ggplot(aes(x = date, y=check)) +
  theme_minimal()+
  geom_point()+
  labs(x="", y="Minutes per day", title="Duolingo English practice time Scatterplot")
```






